%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

% \profilepic{sceon.jpg} % Profile picture
\cvname{Sċéon Morrissette} % Your name
\cvjobtitle{\normalsize{\centerline{Founder | Systems Architect}}} % Job title/career

\cvaddress{Reno, NV} % Short address/location, use \newline if more than 1 line is required
\cvnumberphone{+1 (775) 354-4343} % Phone number
\cvsite{https://eons.llc} % Personal website
\cvmail{sceon@eons.llc} % Email address

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	 ABOUT ME
%----------------------------------------------------------------------------------------

\aboutme{Sċéon: interdisciplinary\_engineer(\\
\hspace*{2em}domain(\\
\hspace*{4em}'biotechnology',\\
\hspace*{4em}'AI systems',\\
\hspace*{4em}'distributed systems',\\
\hspace*{4em}'cloud infrastructure',\\
\hspace*{4em}'business operations'\\
\hspace*{2em}),\\
\hspace*{2em}build(\\
\hspace*{4em}'durable systems',\\
\hspace*{4em}'scalable platforms',\\
\hspace*{4em}'high-performing teams'\\
\hspace*{2em})\\
)\\
I take responsibility for complex systems from initial design through deployment and long-term evolution.}

%----------------------------------------------------------------------------------------
%	 SKILLS
%----------------------------------------------------------------------------------------

% Skills grouped by category
\skills{%
	{\textbf{Platform Architecture}/
		\textbullet\ Kubernetes (multi-node)\\\hspace*{1em}
		\textbullet\ Secure multi-tenant infra\\\hspace*{1em}
		\textbullet\ Networking\\\hspace*{1em}
		\textbullet\ CI/CD
	},%
	{\textbf{Distributed Systems}/
		\textbullet\ Runtime \& packaging design\\\hspace*{1em}
		\textbullet\ Service orchestration\\\hspace*{1em}
		\textbullet\ Production reliability
	},%
	{\textbf{Programming \& Tooling}/
		\textbullet\ C++, Python, PHP, JavaScript\\\hspace*{1em}
		\textbullet\ Custom language/runtime development
	},%
	{\textbf{Embedded Systems}/
		\textbullet\ Low-level drivers (SPI, I2C, PWM)\\\hspace*{1em}
		\textbullet\ Robotics integration
	},%
	{\textbf{Leadership}/
		\textbullet\ Team building\\\hspace*{1em}
		\textbullet\ Mentoring\\\hspace*{1em}
		\textbullet\ Project management
	},%
	{\textbf{Systems Analysis \& Debugging}/
		\textbullet\ Experiment design\\\hspace*{1em}
		\textbullet\ Root-cause isolation\\\hspace*{1em}
		\textbullet\ Performance profiling\\\hspace*{1em}
		\textbullet\ Reliability validation
	}%
}

%------------------------------------------------

% Skill text section, each skill must have a value between 0 an 6
%\skillstext{{Hacker/},{Scientist/},{Manager/}}

%----------------------------------------------------------------------------------------

\makeprofile % Print the sidebar

%----------------------------------------------------------------------------------------
%	 INTERESTS
%----------------------------------------------------------------------------------------

%\section{Interests}
%
%I'm interested in working on any difficult problems and learning as much as I can.
%Generally, this includes any kind of engineering and theory of biology through math.


%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{twenty}
	\twentyitem{2024--now}{Software Engineer}{\textbf{Uplynx}}{%
		\hangindent=1em\hangafter=0\textbullet\ Architected and delivered an offline-capable PWA for a field-operations platform supporting multi-state service workflows across distributed offices.\par
		\hangindent=1em\hangafter=0\textbullet\ Owned fullstack implementation (data modeling, API design, sync strategy, and deployment), enabling reliable execution in low-connectivity environments.\par
		\hangindent=1em\hangafter=0\textbullet\ Built a durable operational foundation currently serving active field staff in multiple locations, with expansion capacity designed into the system architecture.\par%
	}
	\twentyitem{2022--2023}{Senior Software Engineer}{\textbf{Zywave}}{%
		\hangindent=1em\hangafter=0\textbullet\ Helped lead development of a high-growth comparative quoting platform where quote volume was a primary business KPI, sustaining thousands of daily transactions and supporting multi-million-dollar premium workflows.\par
		\hangindent=1em\hangafter=0\textbullet\ Sole on-call engineer responsible for production stability and incident response.\par
		\hangindent=1em\hangafter=0\textbullet\ Led Snowflake integration initiatives and mentored junior engineers across sprint planning and architectural decisions.\par%
	} 
	\twentyitem{2020--now}{Founder \& CEO}{\textbf{eons LLC}}{%
		\hangindent=1em\hangafter=0\textbullet\ Architect and operate a multi-tenant computing platform spanning a 9-node Kubernetes cluster and additional firewall/management servers supporting production client workloads.\par
		\hangindent=1em\hangafter=0\textbullet\ Design and maintain the Elder programming language and associated tooling (EBBS build system, packaging model, container images, and self-hosted Git infrastructure).\par
		\hangindent=1em\hangafter=0\textbullet\ Built and operated a revenue-generating platform with sustained growth (+153\% YoY gross charges over the last 12 months), while owning roadmap, budgets, and client delivery.\par%
	}
	\twentyitem{2017--2021}{Research Associate}{\textbf{ZeaKal}}{%
		\hangindent=1em\hangafter=0\textbullet\ Contributed to the design and execution of a genetic engineering pipeline across lab, greenhouse, and study execution; managed personnel and resources.\par
		\hangindent=1em\hangafter=0\textbullet\ Built and verified data-processing tooling (Excel/Python) to automate experimental digestion and speed time-to-results.\par
		\hangindent=1em\hangafter=0\textbullet\ Hosted internal research data servers to support collaboration across a distributed team.\par%
	}
	\twentyitem{2015--2019}{Lead Software Engineer}{\textbf{Brain2Bot}}{%
		\hangindent=1em\hangafter=0\textbullet\ Designed and deployed cross-platform C++/Qt software for modular robotics systems.\par
		\hangindent=1em\hangafter=0\textbullet\ Developed low-level drivers and integrations for PWM, SPI, and I2C modules across custom hardware.\par
		\hangindent=1em\hangafter=0\textbullet\ Owned system integration from hardware interfaces through user-facing software workflows.\par%
	}
\end{twenty}


%----------------------------------------------------------------------------------------
%	 EDUCATION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{twenty} % Environment for a list with descriptions
	\twentyitem{2013-2017}{B.S. Biochemistry \& Molecular Biology}{University of Nevada, Reno}{Thesis: "Overexpression of DGAT1 and Modified Cysteine Soy Oleosin Increases Oil Content in the Green Tissue of \textit{Arabidopsis thaliana}", also earned a minor in mathematics.}
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}


%----------------------------------------------------------------------------------------
%	 AWARDS
%----------------------------------------------------------------------------------------

% \section{Achievements}

% \begin{twenty} % Environment for a short list with no descriptions
% 	\twentyitem{2016}{Secretary \& Director}{Reno Video Game Symphony}{Designed \& implemented a constitution for the Reno Video Game Symphony and made the organization 501(c)(3) nonprofit.}
% 	\twentyitem{2014}{Eagle Scout}{Boy Scouts of America}{Eagle scout project was painting a map of the United States at Virginia Palmer Elementary School.}
% \end{twenty}

%----------------------------------------------------------------------------------------
%	 PROJECTS
%----------------------------------------------------------------------------------------

% \section{Projects by Release Date}

% \begin{twenty} % Environment for a short list with no descriptions
% 	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
% 	\twentyitem{in progress}{Develop Biology}{\href{https://develop,bio}{https://develop.bio}}{Open source, backwards compatible, recursive hypergraph with reflection and a frontend as my own programming language.}
% 	\twentyitem{2021}{Eons Basic Build System}{\href{https://github.com/eons-dev/bin\_ebbs}{https://github.com/eons-dev/bin\_ebbs}}{Python devops with runners for any process \& any language.}
% 	% \twentyitem{2021-2022}{Mood Recorder}{\href{https://moodrecorder.org}{https://moodrecorder.org}}{Progressive Web App for improving emotional health.}
% 	\twentyitem{2020}{Web Infrastructure}{\href{https://web.infrastructure.tech/architecture/}{https://web.infrastructure.tech/architecture/}}{Globally distributed Kubernetes cluster \& auto-managed WordPress.}
% \end{twenty}

%----------------------------------------------------------------------------------------
%	 OTHER INFORMATION
%----------------------------------------------------------------------------------------

\section{Latest}

Get the latest version of this resume at \href{https://github.com/eons44/resume.doc}{https://github.com/eons44/resume.doc}\\
\textbf{References are available upon request} (they will not be stored on the public repo).

\end{document} 
